%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Ram Nikhil Teja Budide} \\ \vspace{1pt}
    Macherla, Guntur, Andhra Pradesh \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 7095657446 ~ \href{mailto:ramnikhil312@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ramnikhil312@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/ram-nikhil-teja-budide-1759761a3/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/ramnikhilteja}}  ~
    \href{https://github.com/RamNikhil4}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/RamNikhil4}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rajiv Gandhi University of Knowledge Technologies}{2020 -- 2024}
      {Bachelor of Technology in Computer Science and Engineering -- CGPA: 7.9/10}{Basar, Telangana}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Actanós}{November 2024 -- Present}
      {Frontend Developer}{Singamaneni Palli, Andhra Pradesh}
      \resumeItemListStart
        \resumeItem{Developed three production applications using React, TypeScript, and TanStack ecosystem for legal tech, document management, and CRM domains.}
        \resumeItem{Built dynamic form builder and email template builder with drag-and-drop functionality, enabling non-technical users to create custom forms and templates efficiently.}
        \resumeItem{Implemented CSV bulk import with PapaParse for importing thousands of contacts and document editor with undo/redo, zoom, and resizable blocks.}
        \resumeItem{Engineered automatic workflow progression in case filing application and developed responsive Actanós company website using Tailwind CSS.}
        \resumeItem{Utilized TanStack Query, Router, and Table for efficient state management, routing, and data visualization while collaborating with cross-functional teams.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Dynamic Form Builder} $|$ \emph{React, TypeScript, Drag-and-Drop, Custom Hooks}}{Personal Project}
          \resumeItemListStart
            \resumeItem{Built a flexible form builder application allowing users to create custom forms through intuitive drag-and-drop interface with real-time preview functionality.}
            \resumeItem{Implemented multiple field types including text inputs, dropdowns, checkboxes, radio buttons, and file uploads with customizable validation rules and styling options.}
            \resumeItem{Designed reusable component architecture with custom React hooks for form state management, field registration, and validation logic.}
            \resumeItem{Added features for form export/import as JSON, conditional field rendering, and responsive design for seamless mobile experience.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Real-Time Chat Application} $|$ \emph{React, TypeScript, WebSockets, Node.js}}{Personal Project}
          \resumeItemListStart
            \resumeItem{Developed full-stack real-time messaging application with WebSocket integration for instant bidirectional communication between multiple users.}
            \resumeItem{Implemented user authentication, chat rooms, private messaging, typing indicators, and online/offline status tracking with persistent message history.}
            \resumeItem{Built responsive chat UI with message threading, emoji support, and file sharing capabilities using modern React patterns and TypeScript for type safety.}
            \resumeItem{Optimized WebSocket connection handling for reconnection logic, message queuing, and efficient data synchronization across clients.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Neural Notes Sync} $|$ \emph{React, PWA, SQL Wasm, OPFS, CRDTs}}{Personal Project}
          \resumeItemListStart
            \resumeItem{Architected a local-first knowledge base using SQLite Wasm and Origin Private File System (OPFS) for high-performance persistent storage.}
            \resumeItem{Implemented conflict-free replicated data types (CRDTs) to handle multi-device synchronization and eventual consistency.}
            \resumeItem{Developed a Progressive Web App (PWA) ensuring complete offline functionality with instant sub-100ms load times.}
          \resumeItemListEnd
          \vspace{-13pt}
          
    \resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript (ES6+), TypeScript, HTML5, CSS3, SQL} \\
     \textbf{Frontend Technologies}{: React.js (Hooks, Context API, Custom Hooks), TanStack Query, TanStack Table, TanStack Router} \\
     \textbf{Styling \& UI}{: Tailwind CSS, CSS Modules, Responsive Design, Mobile-First Design} \\
     \textbf{Backend (Familiar)}{: Node.js, Express.js, Hono, REST APIs, WebSockets} \\
     \textbf{Databases (Familiar)}{: MongoDB, PostgreSQL} \\
     \textbf{Tools \& Libraries}{: Git, GitHub, VS Code, PapaParse, Postman, npm/yarn, Webpack} \\
     \textbf{Core Competencies}{: Component Architecture, State Management, API Integration, Performance Optimization, Code Reviews} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}